### 2020-04-26 thesis_template/0_Prelim/abs.tex
labled documentation

Many existing big data processing tools are developed with application languages. 
Dataflow platform such as Hadoop MapReduce,  Apache Spark, and Apache Flink 
developed on Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer. 
This eases development processes and distribution of these tools and gives by eliminating manual memory management and 
platform dependency.

However, the automated memory strategy, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
Apache Spark and Apache Flink use complex objects to manipulate and transfer data. 
Generating many of these complex objects in memory forces GC to rearrange states of memory frequently waisting computation. 
Keeping these objects in memory for long period of time may trigger stop-the-world where the JVM stops application from running to
execute a GC.

>>>>

Many existing Big Data processing tools are developed with application languages. 
Dataflow platform such as Hadoop MapReduce,  Apache Spark, and Apache Flink 
developed on Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer. 
This eases development processes and distribution of these tools by eliminating manual memory management and 
platform dependency.

However, the automated memory strategy, such as Garbage Collection (GC), may lead significant overhead in Big Data processing. 
Apache Spark and Apache Flink use complex objects to manipulate and transfer tremendous amount of data. 
Generating many of these complex objects in memory forces GC to rearrange the objects in memory frequently waisting computation. 
Keeping these objects in memory for long period of time may trigger stop-the-world where the JVM stops application from running to
execute a GC.

### 2020-04-26 thesis_template/1_Intro/intro.tex
labled documentation

\section{Motivation}
\label{sec:history}
Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations and leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies democratized data driven businesses by 
eliminating significant amount of initial investment.

However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
If your process of data analysis is too long or need to use a number of cluster with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

\section{Problem Description}
\label{sec:history}

>>>>

\section{Motivation}
\label{sec:motivation}
Importance of cluster computing tool for Big Data Analysis has been increasing as amount, value, use of data has increased. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies have democratized data driven businesses by 
eliminating significant amount of initial investment.

However these technologies do not come for free; we need to pay money for use of these resources. Usually, user needs to pay depending on use of computational resources. 
If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

\section{Problem Description}
\label{sec:probdesc}

### 2020-04-26 thesis_template/3_Body/chapter/concept.tex
labled documentation

\subsection{Type of Variable}
\label{sec:history}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable types for operation in most case.

@@

\subsection{Reference Count}
\label{sec:history}
Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
However, the possible problem regarding to Rc is the cost for tracking the number of references. 
Having this assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
This is explained in section 3.2.

\subsection{Multithreading}
\label{sec:history}
In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
Therefore, one can implement various concurrent codes for the same purpose with different memory management strategies. 
The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).

@@

\subsection{Tree-aggregate}
\label{sec:history}
Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.

Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib). 
The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.

Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
When it aggregates objects in RDD, copy of objects in source vector should be performed to construct intermediate aggregated data structure.
In another way, one can use reference to the objects to perform aggregation instead of copying the values themselves.
In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.

@@

\subsection{K-Nearest-Neighbors}
\label{sec:history}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted category.

@@

Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory.
The detail implementation is explained in section3.2.

\subsection{Complex Objects}
\label{sec:history}
To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

 \subsection{Wikipedia Data Sets}
 \label{sec:history}
 Wikipedia page data sets are used to perform document classification with KNN. 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.

 \subsection{Experimental Details}
 Our experiments are run on three types of VM instances on Google Cloud Platform: 
 n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
 All of the experiments described are performed 5 times. 
 In this thesis, we present the average of 5 separate runs for each experiment.
\clearpage

>>>>

\subsection{Type of Variable}
\label{sec:concept_diffval}
In Rust, there are three variable types: owner, reference, and slice (only for sequence of values). 
A developer is sometimes forced to use specific variable types. For example, some of methods are only implemented to specific variable types.
However, one can select any variable types for operation in most case.

@@

\subsection{Reference Count}
\label{sec:concept_refcount}
Reference is useful to avoid movement of ownership. However, one needs to track its lifetime and explicitly includes it in code, 
because Rust compiler cannot infer it. This can be another encumbrance. We can instead acquire multiple owners to single value by using Reference Counting (Rc). 
By leveraging Rc, a value can be shared like what borrowing plays the role in Rust programming.

The difference is that Rc checks number of owner pointing to the actual data and makes sure the data is not deleted 
until all the owners are dereferenced. Using Rc is sometimes preferable approach for developers especially when lifetime planning is extremely difficult.
However, the possible problems regarding to Rc are the cost for tracking the number of references and allocating memory on heap instead of stack.
Having these assumption, an experiment is conducted to examine difference of runtime performance of dropping reference and Rc. 
This is explained in section 3.2.

\subsection{Multithread}
\label{sec:concenpt_multithreading}
In Rust programming, writing concurrent code is relatively easy. The care Rust takes with reference, mutability, and lifetimes is valuable enough in single-threaded programs, 
but it also is in concurrent programming. Rust has tools to write concurrent code, such as threads, locks, atomic reference. 
One can implement various concurrent codes for the same purpose with different memory management strategies. 
The most ubiquitous tool used in Rust concurrent code is Atomic Reference Counting (Arc).

@@

\subsection{Tree-aggregate}
\label{sec:concept_treeagg}
Finally, we implement some of algorithm common in Big Data processing. One of them is tree-aggregate.

Tree-aggregate is a communication patten heavily used for Machine Learning algorithm in Spark (MLlib \cite{DBLP:journals/jmlr/MengBYSVLFTAOXX16}). 
The topology of aggregation patterns in Apache Spark are shown in Figure~\ref{fig:aggregationk_patttern}. 
In the traditional aggregation function in Spark, results of aggregation in all executor clusters are sent to the driver. 
That is why this operation suffers from the CPU cost in merging partial results and the network bandwidth limit.
Tree-aggregate is a communication pattern which overcomes these problems by breaking aggregate operation in multi-level represented like tree structure.

Spark generates intermediate objects from RDDs. In Tree-aggregation, aggregated HashMap like data structure is created in each thread or node. 
When it aggregates objects in RDD, copy of objects should be performed to construct intermediate aggregated data structure.
In another possible way that might be implemented, one can use reference to the objects to perform aggregation instead of copying the values themselves.
In Rust, we can clone or get Arc (Rc if in single thread) of objects to implement these operations.

@@

\subsection{K-Nearest-Neighbors}
\label{sec:concept_history}
The other algorithm common in Big Data processing is K-nearest-neighbors (KNN). KNN is a traditional Machine Learning algorithm which classify targets into categories. 
In training KNN, it simply stores all available training data without calculation. At prediction phase, targets are given and similarity measures are calculated. 
Based on these similarities, the algorithm selects \(K\) (user-defined number) training observations similar to the each target. 
Then, it checks corresponding categories of the \(K\) observations to determine predicted category.

@@

Our KNN algorithms are implemented with batch processing. In query phase, we control batch size to examine how size of objects allocated simultaneously in memory has impact to algorithm's runtime performance.
The detail implementation is explained in section3.2.

\subsection{Complex Objects}
\label{sec:concept_history}
To conduct experiments for above concepts, we use the 4 types of complex object: CustomerOwned, CustomerBorrowed, CustomerSlice, and CustomerRc. 
These object contains other type of object: OrderOwned, OrderBorrowed, OrderSlice, and OrderRc.
The representation of these objects are shown in Figure~\ref{fig:customer} and Figure~\ref{fig:order}. 
Three Customer objects have 15 fields: 3 fields for i32, 3 fields for f64, 8 fields for String, and 1 field for Order object.
All of fields of CustomerOwned and OrderOwned are owned by the object. On the other hand, fields of CustomerBorrowed, CustomerSlice, OrderBorrowed, and OrderSlice are borrowed. 
Reference of slice of values are used as the fields and owner of actual values are stored differently in source Vec. 
CustomerRc acquires Rc of values used for its fields from the source Vec.

@@

 \subsection{Wikipedia Data Sets}
 \label{sec:concept_dataset}
 Wikipedia page data sets are used to perform document classification with KNN. 
 \(10^5\) pages are used for training data set, and 18724 pages are used for target.

 \subsection{Experimental Details}
 \label{sec:concept_expdetail}
 Our experiments are run on three types of VM instances on Google Cloud Platform: 
 n1-standard-1 which has 1 vCPU, 3.75 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-4 which has 4 vCPU, 15 GB RAM, and 10 GB Standard persistent disk, 
 n1-standard-8 which has 8 vCPU, 30 GB RAM, and 10 GB Standard persistent disk,  
 All of the experiments described are performed 5 times. 
 In this thesis, we present the average of 5 separate runs for each experiment.
\clearpage
